\documentclass{article}

\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsthm}

\newtheorem{definition}{Definition}
\newtheorem{thm}{Theorem}
\title{Semigroups}
\author{Sasha Beliaev}
\begin{document}
\maketitle
\begin{definition}
    Let $(S, \cdot)$ be a set with binary operation. 
    Then $S$ called a \textbf{semigroup}, if operation $\cdot$ is accociative, namely,
    \[
        (a\cdot b)\cdot c= a\cdot (b\cdot c)
        \] 
    for all elements $a, b, c$ from $S$.
\end{definition}
\begin{definition}
    Let $S$ be a semigroup. If it has a unit and every element 
    has an inverse, or formally:
    \begin{align}
        \exists e&\in S\;\forall x\quad e\cdot x=x\cdot e = x\\
        \forall x&\in S\;\exists x'\quad x\cdot x'= x'\cdot x = e
    \end{align}
    then it is called a \textbf{group}.
\end{definition}
\begin{thm}
    Let S be a semigroup such that
    \begin{align}
        \exists e_l\in S\;\forall x\;\; e_l\cdot x &= x\\
        \forall x\;\exists x^{-1}\;\; x^{-1}\cdot x &= e_l 
    \end{align}
    Then $S$ is a group.
\end{thm}
\begin{proof}
There are no idempotents in $S$ except $e_l$. Indeed, if $a=a\cdot a$ is an 
idempotent, then
\[
a = e_l\cdot a = (a^{-1}\cdot a)\cdot a = 
a^{-1}\cdot(a\cdot a) = a^{-1}\cdot a = e_l
\]
Lets check that left inverse is also a right inverse. For any $x\in S$ we have
\[
    (x\cdot x^{-1})\cdot (x\cdot x^{-1}) = x\cdot(x^{-1}\cdot x)\cdot x^{-1} =
    x\cdot e_l\cdot x^{-1} = x\cdot x^{-1}
\]
Therefore $x\cdot x^{-1}$ is an idempotent and must be equal to $e_l$.
Lets show that the left unit $e_l$ is a right unit. For any $x\in S$
\[
    x\cdot e_l = x\cdot(x^{-1}\cdot x) = (x\cdot x^{-1})\cdot x = 
    e_l\cdot x = x
\]
\end{proof}

\begin{thm}
    Let $S$ be a semigroup with the property:
    \[
        aS = S,\;Sa=S    
    \]
    for all $a\in S$. Then S is a group.
\end{thm}
\begin{proof}
    We show that $S$ has a left unit and a left inverse.

    Choose an arbitrary element $a\in S$. There exists $e_a\in S$ such that $e_a\cdot a = a$.
    Lets check that $e_a$ is a left unit. For every $x\in S$ there exists 
    $y\in S$ such that $x = a\cdot y$. Then
    \[
        e_a\cdot x = e_a\cdot(a\cdot y) = (e_a\cdot a)\cdot y=a\cdot y=x
        \]
    Therefore, $e_a$ is a left unit.

    If $x\in S$, then there is an element $y$ such that $y\cdot x=e_a$, i.e. $y=x^{-1}$
    is a left inverse for $x$.
\end{proof}
\end{document}